---
title: Blog 1
author: Peimin Lin
date: '2020-08-28'
slug: blog-1
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2020-09-02T19:27:06+10:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE,
  warning = FALSE, 
  fig.align = "center")
library(tibble)
library(timevis)
library(tidyverse)
library(broom)
library(lubridate)
library(zoo)
library(coronavirus)
library(widgetframe)
library(formattable)
library(bookdown)
```

```{r read_data}
case <- read_csv("COVID19BE_CASES_AGESEX.csv")
mort <- read_csv("COVID19BE_MORT.csv")
data("coronavirus")
```

The blog is a research about coronavirus(COVID-19) in Belgium from March 2020 to August 2020 and used the data source from [Kaggle]( https://www.kaggle.com/evgeniako/covid19-in-belgium) and used  the dataset from package *coronavirus*. 

You can visualise the number of COVID-19 cased confirmed in Belgium from March to August 2020 in Figure \@ref(fig:active). It shows that April was the most seriousness month that have the largest infected population. Since then, people started pay attention and took anti-epidemic action and the confirmed cases got a good result. However, there are still have high number of confirmed cases. 

```{r case_tidy}
tidy_case <- case %>% mutate(MONTH = month(DATE),
                             YEAR = year(DATE)) %>% 
 count(MONTH,YEAR, name = "NUMBER")%>%
  drop_na(MONTH) 
```

```{r tibble}
tibble <- within(tidy_case, Date <- sprintf("%d-%02d", YEAR, MONTH)) %>% mutate(start = Date, end = NA)
```

```{r active, fig.cap = "Cases confrimed in Belgium since March 2020"}
active <- tibble %>%
  dplyr::select( NUMBER, start, end) %>% 
  rename(content = NUMBER)
timevis(active, showZoom = FALSE, height = "150px")
   
```

For further research, it found that the elder got higher infected rate, the table show below listed confirmed cases in difference provinces and regions and difference age group. It shows that the largest number were from 80-89 age group in every region in April. 


```{r format}
format <- case %>% 
  mutate(MONTH = month(DATE)) %>%
 count(MONTH,REGION,PROVINCE, AGEGROUP,name = "NUMBER") %>%
  drop_na(PROVINCE, REGION,AGEGROUP)%>% 
  arrange(desc(NUMBER)) %>%
  head(10)
```

```{r compare}
compare <- format %>% 
  as.data.frame() %>%
rownames_to_column("Variables") %>%
formattable(align = "r",
            list(area(col = 6) ~ color_tile("#7DCEA0","#FA614B66")))
compare
```

We found that not only did the elder would easier infected, but also got a higher death rate. Figure \@ref(fig:facet) shown below that number of mortality in three regions in Belgium, all the age group people in the lists and especially in the elder group. Brussels is the least number of mortality among the data set. 


```{r mort}
tidy_mort <- mort %>% mutate(MONTH = month(DATE)) %>% 
 count(MONTH,REGION, AGEGROUP,name = "NUMBER") %>%
  drop_na(AGEGROUP)
```

```{r facet, out.width = "100%", fig.cap="Mortaity numbers from March to August in three reigions" }
death <- ggplot(tidy_mort,
       aes(x= MONTH, y = NUMBER, fill = REGION)) +
  geom_col(position = "dodge") +
  facet_wrap(REGION~AGEGROUP,nrow = 3)
death
```

```{r second}
second <- coronavirus %>% 
  filter(date>= "2020-03-01") %>%
  dplyr::select(country, type, cases, date) %>%
  mutate(month = month(date))%>%
  group_by(country, type, month) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type,
              values_from = total_cases)%>%
  mutate(death_rate = death/confirmed*100,
         recovered_rate = recovered/confirmed*100)%>%
  mutate_if(is.numeric, round, digits = 2) %>%
  dplyr::select(country, month,death_rate, recovered_rate) %>%
  filter(country %in% c("US","China","Belgium"))
```

Compare with United State and China which are the country got serious epidemic, we calculate the death rate and recovery rate. The interactive table shows below that Belgium got the second highest death rate in April. During this research, I found an article online said that Belgium got the highest death rate around the world. What made Belgium rank the first place? If you interested about it, you can spend few minutes to have a look [Is Belgium the world's deadliest COVID-19 country or just the most honest?](https://www.smh.com.au/world/europe/is-belgium-the-world-s-deadliest-covid-19-country-or-just-the-most-honest-20200522-p54voq.html) 

Belgium is a beautiful country, it is famous for its chocolate and it has plenty of historical treasures. Hope the epidemic will end soon and I will have the opportunity to travel.


```{r dt}
dtable <- DT::datatable(second, options = list(pageLength = 5), width = "500px", caption = "Comparison betwee US and China from March to July")
frameWidget(dtable)
```


# Reference

Allaire, J, Y Xie, J McPherson, J Luraschi, K Ushey, A Atkins, H Wickham, J Cheng, W Chang, and R Iannone (2020). **rmarkdown: Dynamic Documents for R.** R package version 2.1. https://rmarkdown.rstudio.com.

Grolemund, G and H Wickham (2011). Dates and Times Made Easy with lubridate. **Journal of Statistical Software 40(3), 1–25.**

Wickham, H, M Averick, J Bryan, W Chang, LD McGowan, R François, G Grolemund, A Hayes, L Henry, J Hester, M Kuhn, TL Pedersen, E Miller, SM Bache, K Müller, J Ooms, D Robinson, DP Seidel, V Spinu, K Takahashi, D Vaughan, C Wilke, K Woo, and H Yutani (2019). Welcome to the tidyverse. **Journal of Open Source Software 4(43), 1686.**

Xie, Y (2020a). **bookdown**: Authoring Books and Technical Documents with R Markdown. R package version 0.18. https://github.com/rstudio/bookdown

Kirill Müller and Hadley Wickham (2020). **tibble**: Simple Data Frames. R package version 3.0.3. https://CRAN.R-project.org/package=tibble

Dean Attali and Almende B.V. (2019). **timevis**:Create Interactive Timeline Visualizations in R.  R package version 0.5. https://CRAN.R-project.org/package=timevis

 David Robinson, Alex Hayes and Simon Couch(2020). **broom**: Convert Statistical Objects into Tidy Tibbles. R package version 0.7.0. https://CRAN.R-project.org/package=broom
 
Achim Zeileis and Gabor Grothendieck (2005). **zoo**: S3 Infrastructure for Regular and Irregular Time Series. **Journal of Statistical Software**, 14(6), 1-27. doi:10.18637/jss.v014.i06

Rami Krispin and Jarrett Byrnes (2020). **coronavirus**: The 2019 Novel Coronavirus COVID-19 (2019-nCoV) Dataset. R package version 0.3.0. https://CRAN.R-project.org/package=coronavirus

Bhaskar Karambelkar (2017). **widgetframe**: 'Htmlwidgets' in Responsive 'iframes'. R package version 0.3.1. https://CRAN.R-project.org/package=widgetframe

Kun Ren and Kenton Russell (2019). **formattable**: Create 'Formattable' Data Structures.https://renkun.me/formattable,

Evgeniya K (2020). **COVID-19 in Belgium.** https://www.kaggle.com/evgeniako/covid19-in-belgium

Yihui Xie, Joe Cheng and Xianying Tan (2020). **DT**: A Wrapper of the JavaScript Library 'DataTables'. R package version 0.15. https://CRAN.R-project.org/package=DT
