---
title: "The impact of Covid-19 in Belgium"
author: "Peimin Lin"
date: '2020-09-12'
output: pdf_document
categories: []
tags: []
subtitle: 'A further research about COVID-19 in Belgium in economic aspect'
summary: ''
authors: [Peimin Lin]
lastmod: '2020-09-14T16:06:03+10:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
slug: blog-2
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE,
  warning = FALSE, 
  fig.align = "center")
library(tidyverse)
library(tidycovid19)
library(bookdown)
library(alfred)
library(lubridate)
library(formattable)
library(stevemisc)
```

<span style="font-size:2em;">This</span> blog is a further research about COVID-19 in Belgium in economic aspect. According to Johns Hopkins University Center for System Science and Engineering invention provided latest version of the data, in the first 180 days Belgium reported death number took a small place in the European Union, however, Belgium took the highest death rate in the world which we found the result in the last blog. 

Figure \@ref(fig:merged) shows reported deaths number in 8 particular European countries in the first 180 days since the epidemic spread out. The graph shows the same trend were increased rapidly in the first 50 days.  

```{r merged,out.width = "80%",fig.cap = "Reported deaths number in European Union."}
merged <- download_merged_data(cached = TRUE, silent = TRUE)
plot_covid19_spread(
  merged, highlight = c("ITA", "BEL","ESP", "GBR", "FRA", "DEU","RUS","SWE"),
  intervention = "lockdown"
)
```

Thanks for lockdown policy in many countries that made the outbreak under control, in Figure \@ref(fig:map) that the latest update in 16th Sep 2020, reported deaths number in European mostly were under 100 cases. In Belgium, it seems that outbreak is under control that keep the number under 10 cases. For further research can have a look at [tidycovid19](https://github.com/joachim-gassen/tidycovid19)

```{r map,out.width = "85%",fig.cap = "Covid19:Reported deaths(new cases per day)"}
map_covid19(merged, type = "deaths", region = "Europe")
```
### Impact of Gross Domestic Product in Belgium
As it surveys an economy ravaged by the disease, Figure \@ref(fig:bgraph) which dataset was downloaded from [Real Gross Domestic Product for Belgium](https://alfred.stlouisfed.org/series?seid=CLVMNACSCAB1GQBElisted) shows that Belgium real gross domestic product (GDP) from first quarter of 2005 to first quarter of 2020. There are two apparent fluctuations that one was from 2008 to 2009 which meet economic crisis, another one was from late 2019 to recent which under COVID-19 outbreak. The horizon line can clearly clarify that first quarter of 2020, GDP for Belgium fell to same level of 2019 which just went through an economic crisis.  

```{r fredbgdp}
fred2020Q1vin <- as_tibble(get_alfred_series("CLVMNACSCAB1GQBE",
                                        observation_start = as.Date("2005-01-01"),realtime_start = "2020-09-08" ))
```

```{r bgraph, out.width = "70%", fig.cap = "Real GDP in Belgium"}
fred2020Q1vin %>%
  ggplot(.,aes(date,CLVMNACSCAB1GQBE)) +
  theme_steve_web() +
  post_bg() +
  scale_x_date(date_breaks = "1 years",
               date_labels = "%Y",
               limits = as.Date(c('2005-01-01','2020-04-01')))+
  geom_rect(data=filter(recessions,year(peak)>2004), inherit.aes=F, 
            aes(xmin=peak, xmax=trough, ymin=-Inf, ymax=+Inf), fill='darkgray', alpha=0.8)+
     geom_line() +
    geom_ribbon(aes(ymin=-Inf, ymax=CLVMNACSCAB1GQBE),
              alpha=0.3, fill="#619CFF")+
labs(title = "GDP From January 1, 2010 to April 1, 2020",
       subtitle = "GDP in Belgium rapidly fell to same level of 2019 which went through an economic crisis.",
       x = "Year", y = "RGDP in Millions of Chained 2010 Euros",
       caption = "Data: source from Eurostat,  http://ec.europa.eu/eurostat/about/overview") + geom_hline(yintercept=87500, linetype="dashed", color = "red") 
```
### Comparison GDP between Euro Aera and Belgium
For a better understanding what impact that virus bring to, I found 19 countries in European aera of their total GDP resources from [Gross Domestic Product for Euro area (19 countries)](https://alfred.stlouisfed.org/series?seid=CLVMEURNSAB1GQEA19). Figure \@ref(fig:gcompare) compared to total GDP of 19 countries in European area, Belgium’s GDP have a same moving trend as European countries. However, in the last two quarter that Belgium has wider variations than normal.

```{r Bgdp-growth}
 fred2020 <-  fred2020Q1vin %>%
  mutate(Diff_growth = CLVMNACSCAB1GQBE - lag(CLVMNACSCAB1GQBE), # Difference in route between years
    BelRate_percent = (Diff_growth /lag(CLVMNACSCAB1GQBE) * 100)) %>%
  mutate_if(is.numeric, round, digits = 3)
```

```{r urogdp-growth}
fredeuro <- as_tibble(get_alfred_series("CLVMEURNSAB1GQEA19",
                                        observation_start = as.Date("2005-01-01"),realtime_start = "2020-09-08" )) %>%
  mutate(EDiff_growth = CLVMEURNSAB1GQEA19-lag(CLVMEURNSAB1GQEA19), # Difference in route between years
   ERate_percent = (EDiff_growth /lag(CLVMEURNSAB1GQEA19) * 100)) %>%
  mutate_if(is.numeric, round, digits = 3)
```

```{r gdpjoin}
joingdp <- left_join(fred2020, fredeuro, by=c("date"="date")) %>%
  dplyr::select(date, BelRate_percent, ERate_percent ) %>%
  rename("Belgium"="BelRate_percent", "Euro"="ERate_percent")
```

```{r gcompare,out.width = "80%",fig.cap = "GDP comparison between Belgium and European Union(19 countries)"}
gdpcom <- ggplot(joingdp, aes(x=date)) +
  geom_line(aes(y = Belgium, colour = "Belgium")) + 
  geom_line(aes(y = Euro, colour = "Euro"))+
  labs(title = "GDP comparison between Belgium and European Union(19 countries)",
       subtitle = "GDP in Belgium flation rate was more than European Union since outbreak.",
       x = "Year", y = "Gradient",
       caption = "Data: source from Eurostat,  http://ec.europa.eu/eurostat/about/overview") 
  
gdpcom 
```
### Impact of Unemployment Rate in Belgium
Meanwhile, Belgium limps back to work after the outbreak, citizens job prospects are truly bleak. It was a period that the workforce as prospective employers mull lay-offs of hiring freezes. For a middle class used to relentlessly strong economic growth, the stock will be great. Figure \@ref(fig:unem) illustrated unemployment rate from first quarter of 2015 to first quarter of 2020, it seems that there was a tendency to decrease unemployment rate since 2015 before epidemic happened. The latest data showed that unemployment rate in Belgium has obvious rose in first quarter in 2020.

```{r fredun}
fredun <- as_tibble(get_alfred_series("LMUNRRTTBEQ156S",
                                        observation_start = as.Date("2015-01-01"), realtime_start = "2020-08-11" ))
```

```{r unem,out.width = "70%", fig.cap = "Unemployment Rate in Belgium"}
fredun %>%
  ggplot(.,aes(date,LMUNRRTTBEQ156S)) +
  theme_steve_web() +
  post_bg() +
  scale_x_date(date_breaks = "1 years",
               date_labels = "%Y",
               limits = as.Date(c('2015-01-01','2020-04-01')))+
  geom_line() +
  geom_point(size=3, shape=22, color="darkred", fill="pink")+
labs(title = "Unemployment Rate From Jan 1 2015 to Apr 1 2020",
       subtitle = "Unemployment rate in Belgium increase significantly since epidemics.",
       x = "Year", y = "Unemployment Rate", caption = "Data: source from Eurostat, http://ec.europa.eu/eurostat/about/overview") 
```
### Comparison Unemployment Rate between Euro Area and Belgium
Comparing unemployment rate around European area, Belgium unemployment rate was higher than average from the past five year but all with a bright future that unemployment rate fell year by year even Figure \@ref(fig:unemcom) shown the gap between Belgium and average European area was increasingly getting bigger. With an unexpected epidemic that every thing seems changed that both have a same turning point since 2020, the tide of unemployment was coming fast and furious and we don’t know how long will this cold wave last. If you have interest for impact in economy, I would like to recommend you to visit [Alfred](https://alfred.stlouisfed.org/) which recorded variance of economy historial data.

```{r freduneuro}
freduneuro <- as_tibble(get_alfred_series("LRHUTTTTEZQ156S",
                                        observation_start = as.Date("2015-01-01"), realtime_start = "2020-08-11",realtime_end = "2020-08-11" )) 

```

```{r joineu}
joineu <- left_join(freduneuro,fredun, by ="date") %>%
  rename("European" ="LRHUTTTTEZQ156S", "Belgium"="LMUNRRTTBEQ156S") %>%
  dplyr::select(date, Belgium, European)%>%
  mutate_if(is.numeric, round, digits = 3)
```

```{r unemcom,out.width = "80%",fig.cap = "Comparison of Unemployment Rate between Belgium and Euro area"}
unemcom <- ggplot(joineu, aes(x=date)) +
  geom_line(aes(y = Belgium, colour = "Belgium")) + 
  geom_line(aes(y = European, colour = "Euro"))+
  labs(title = "Comparison Unemployment rate between Euro area and Belgium",
       subtitle = "Unemployment rate appeared same trend during these year.",
       x = "Year", y = "Unemployment Rate", caption = "Data: source from Eurostat, http://ec.europa.eu/eurostat/about/overview") 
  
unemcom
```

There is no doubt that virus has hit every country hard and it is a big question that we don’t know how bad will COVID-19 be for the economy around the world. There are so many bad news in 2020 and hopefully we can get COVID-19 vaccine soon and pull through together. 

# Reference
Kun Ren and Kenton Russell (2019). **formattable**: Create 'Formattable' Data Structures.https://renkun.me/formattable,

Allaire, J, Y Xie, J McPherson, J Luraschi, K Ushey, A Atkins, H Wickham, J Cheng, W Chang, and R Iannone (2020). **rmarkdown: Dynamic Documents for R.** R package version 2.1. https://rmarkdown.rstudio.com.

Grolemund, G and H Wickham (2011). Dates and Times Made Easy with lubridate. **Journal of Statistical Software 40(3), 1–25.**

Wickham, H, M Averick, J Bryan, W Chang, LD McGowan, R François, G Grolemund, A Hayes, L Henry, J Hester, M Kuhn, TL Pedersen, E Miller, SM Bache, K Müller, J Ooms, D Robinson, DP Seidel, V Spinu, K Takahashi, D Vaughan, C Wilke, K Woo, and H Yutani (2019). Welcome to the tidyverse. **Journal of Open Source Software 4(43), 1686.**

Joachim Gassen (2020). **tidycovid19**: Download, Tidy and Visualize Covid-19 Related Data. R package version 0.0.0.9000.

Steve Miller (2020). **stevemisc**: Miscellaneous Functions/Data That Only Steve Finds Useful. R package version 0.1.17.
  
Xie, Y (2020a). **bookdown**: Authoring Books and Technical Documents with R Markdown. R package version 0.18. https://github.com/rstudio/bookdown

Onno Kleen (2020). **alfred**: Downloading Time Series from ALFRED Database for Various Vintages. R package version 0.1.8. https://CRAN.R-project.org/package=alfred
